A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\section{Results and Discussion}\label{section:results_discussion}

>>>>

\section{Results and Discussion}\label{section:results_discussion}
After reduction of dimensionality of the permeability dataset using the methods described in Sections~\ref{subsection:pcspaces} and \ref{subsection:model}), numerical simulations were performed with Fluidity/IC-FERST model (see Section~\ref{section:mathematical_model} and \cite{Gomes_2017, jackson_2013,salinas_2018}).
